### 2014-04-02 Docs/architecture/architecture.tex
more indexing

The global index space covers the entire domain at a given resolution.
For a simulation setup with {\tt n\_cellx = 32} and {\tt n\_celly =
  32}, the coarsest level (level 1) has $32 \times 32$ zones, and the
global index space will run from $0, \ldots, 31$ in each coordinate
direction.  Level 2 will have a global index space running from $0,
\ldots, 63$ in each coordinate direction (corresponding to $64 \times
64$ zones if fully refined), and level 3 will have a global index
space running from $0, \ldots, 127$ in each coordinate direction
(corresponding to $128\times 128$ zones if fully refined).

@@

For spherical problems, the base state resolution, $\Delta r$, is
generally picked to be finer than the Cartesian grid resolution,
$\Delta x$, i.e.\ $\Delta r < \Delta x$.  The ratio is controlled
by the parameter {\tt drdxfac}.

@@

      A runtime parameter, {\tt use\_eos\_coulomb}, is defined in
      this EOS to enable/disable Coulomb corrections.

@@

This equation of state takes several runtime parameters that can set the
$\gamma_i$ for a specific species:
\begin{itemize}
\item {\tt eos\_gamma\_default}: the default $\gamma$ to apply for
  all species
\item {\tt species\_X\_name} and {\tt species\_X\_gamma}: set the $\gamma_i$
  for the species whose name is given as {\tt species\_X\_name} to the
  value provided by {\tt species\_X\_gamma}.  Here, {\tt X} can be one
  of the letters: {\tt a}, {\tt b}, or {\tt c}, allowing us to specify
  custom $\gamma_i$ for up to three different species.
\end{itemize}

>>>>

The global index space covers the entire domain at a given resolution.
For a simulation setup with \runparam{n\_cellx = 32} and \runparam{n\_celly =
  32}, the coarsest level (level 1) has $32 \times 32$ zones, and the
global index space will run from $0, \ldots, 31$ in each coordinate
direction.  Level 2 will have a global index space running from $0,
\ldots, 63$ in each coordinate direction (corresponding to $64 \times
64$ zones if fully refined), and level 3 will have a global index
space running from $0, \ldots, 127$ in each coordinate direction
(corresponding to $128\times 128$ zones if fully refined).

@@

For spherical problems, the base state resolution, $\Delta r$, is
generally picked to be finer than the Cartesian grid resolution,
$\Delta x$, i.e.\ $\Delta r < \Delta x$.  The ratio is controlled
by the parameter \runparam{drdxfac}.

@@

      A runtime parameter, \runparam{use\_eos\_coulomb}, is defined in
      this EOS to enable/disable Coulomb corrections.

@@

This equation of state takes several runtime parameters that can set the
$\gamma_i$ for a specific species:
\begin{itemize}
\item \runparam{eos\_gamma\_default}: the default $\gamma$ to apply for
  all species
\item \runparam{species\_X\_name} and \runparam{species\_X\_gamma}: set the $\gamma_i$
  for the species whose name is given as {\tt species\_X\_name} to the
  value provided by {\tt species\_X\_gamma}.  Here, {\tt X} can be one
  of the letters: {\tt a}, {\tt b}, or {\tt c}, allowing us to specify
  custom $\gamma_i$ for up to three different species.
\end{itemize}

### 2014-04-02 Docs/unit_tests/unit_tests.tex
more indexing

  This test initializes a Gaussian density field (no other scalar
  quantities are used) and a uniform velocity field in any one of the
  coordinate directions.  The Gaussian profile is advected through the
  period domain exactly once and the error in the density profile (L2
  norm) is computed.  The driver for this problem does this for every
  dimension twice (once with a positive velocity and once with a
  negative velocity), and loops over all advection methods ({\tt
  ppm\_type = 0,1,2} and {\tt bds\_type = 1}).  After all coordinate
  directions are tested, the norms are compared to ensure that the
  error does not show any directional bias.

>>>>

  This test initializes a Gaussian density field (no other scalar
  quantities are used) and a uniform velocity field in any one of the
  coordinate directions.  The Gaussian profile is advected through the
  period domain exactly once and the error in the density profile (L2
  norm) is computed.  The driver for this problem does this for every
  dimension twice (once with a positive velocity and once with a
  negative velocity), and loops over all advection methods
  (\runparam{ppm\_type} {\tt = 0,1,2} and \runparam{bds\_type} {\tt = 1}).  After
  all coordinate directions are tested, the norms are compared to
  ensure that the error does not show any directional bias.
